---
title: "Homework 6"
author: "Yiyang LIU"
date: "2019/11/20"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(broom)
library(rvest)
library(modelr)
library(mgcv)
knitr::opts_chunk$set(
 echo = TRUE,
 fig.width = 8, 
 fig.height = 6,
 fig.asp = 0.618,
 out.width = "90%")
theme_set(theme_bw() + 
          theme(legend.position = "bottom",
                legend.title = element_blank(),
                plot.title = element_text(hjust = 0.5, size = 15),
                plot.subtitle = element_text(hjust = 0.5, size = 12)))

```

# Problem 1

### Load and clean the data for regression analysis
```{r}
bw = read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    babysex = factor(babysex, levels = c("1", "2")),
    frace = factor(frace, levels = c("1", "2", "3", "4", "8", "9")),
    malform = factor(malform, levels = c("0", "1")),
    mrace = factor(mrace, levels = c("1", "2", "3", "4", "8"))
  ) 

sum(is.na(bw))
```

There is no NAs in the dataset.


### Propose a regression model for birthweight. 

```{r}
fit = lm(bwt ~ ., data = bw) %>%
  step(direction = "backward")
```

First I use "Stepwise Regression" to choose my model. According to the results above, I choose `bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken`.

```{r}
mymodel = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = bw)
summary(fit)
```

The adjustted R-square of my model is 0.72 and the p-value of F test is significantly less than 0.05.

### plot of model residuals against fitted values

```{r}
bw %>% 
  add_predictions(fit) %>% 
  add_residuals(fit) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = lm, color = "red")+
  labs(
    titles = "Residuals VS fitted values",
    x = "Fitted values",
    y = "Residuals"
  )
```

### Compare my model to two others

* My model: `bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken`

* Model 1: `bwt ~ blength + gaweeks`

* Model 2: `bwt ~ babysex + blength + bhead + babysex * blength + babysex * bhead + blength * bhead + babysex * blength * bhead`

```{r}
set.seed(1)

crossv_mc(bw, 100) %>% 
    mutate(train = map(train, as_tibble),
           test = map(test, as_tibble)) %>% 

    mutate(mymodel = map(train, ~lm(bwt ~ babysex + bhead + blength + gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x)),
           model_1 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
           model_2 = map(train, ~lm(bwt ~ babysex + blength + bhead + babysex * blength + babysex * bhead + blength * bhead + babysex * blength * bhead, data = .x))) %>% 
    mutate(rmse_mymodel = map2_dbl(mymodel, test, ~rmse(model = .x, data = .y)),
           rmse_model_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
           rmse_model_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y))) %>% 
  select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = str_replace(model, "rmse_", ""),
         model = fct_inorder(model)) %>% 
  
  ggplot(aes(x = model, y = rmse, fill = model)) + 
  geom_violin(alpha = .6, color = "blue") + 
  labs(title = "Compare fitted model to two others",
       x = "Modle",
       y = "RMSE")
```

According to the plot, my model has the smallest overall RMSE among the 3 models so I can conclude that my model has more predictive accurary than the other two. Model 1 is the poorest when being used to  describing what factors can affect baby’s birthweight based on this dataset.

# Problem 2

### Load data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

### A simple linear regression with `tmax` as the response and `tmin` as the predictor

```{r}
fit = lm(tmax ~ tmin, data = weather_df)
summary(fit)
```

The fitted model is $\widehat Y =7.21 + 1.04\widehat X $ (Y=tmax, X=tmin)

### Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of two qauntities

* $\widehat {r}^2$

* $\log (\widehat{\beta_o} \times \widehat{\beta_1})$

```{r}
bootstrap = function(x){
  
  model_1 =
    x %>% 
    broom::tidy()
  model_2 =
    x %>%
    broom::glance()
  
  tibble(
    r_squared = pull(model_2, adj.r.squared),
    log_beta0_beta1 = log(pull(model_1, estimate)[1] * pull(model_1, estimate)[2]))
  
}

estimates = 
 weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~ lm(tmax ~ tmin, data = .x)),
    results = map(models, bootstrap)) %>% 
  unnest(results) %>%
  select(-strap, -models) 

estimates[1:6,] %>%
  rename("Linear model" = `.id`) %>%
  knitr::kable(align = 'c')
```

### The distribution of r_square

```{r}
estimates %>% 
  ggplot(aes(x = r_squared)) +
  geom_density(fill = "light pink", color = "light pink", alpha = .6, size = 1.3) +
  labs( x = expression(""~hat(r)^2~""),
       title = expression("Distribution of "~hat(r)^2~""),
       y = "Density")
```


### The distribution of log(beta_0*beata_1)

```{r}
estimates %>% 
  ggplot(aes(x = log_beta0_beta1)) +
  geom_density(fill = "light blue", color = "light blue", alpha = .6, size = 1.3) +
  labs(x = expression("log("~hat(beta)[0]~"*"~hat(beta)[1]~")"),
       title = expression("Distribution of log("~hat(beta)[0]~"*"~hat(beta)[1]~")"),
       y = "Density")
```

Both of the distribution of two estimates are a little left skewed, indicating that there might be some outliers in the dataset.

### 95% confidence intervals

```{r}
r_square_interval = quantile(pull(estimates, r_squared), c(0.025,0.975))
log_b0_b1_interval = quantile(pull(estimates, log_beta0_beta1), c(0.025,0.975))
rbind(r_square_interval, log_b0_b1_interval) %>% 
  knitr::kable(format = "html", align = 'c', caption = "95% confidence interval for estimates")
```

